### 2012-10-10 1.tex
Writing on front matter, chapters 1-4

\chapter{A generative theory of phonotactics and phonotactic learning}

\section{\emph{Táxis} and generativity}

%\emph{τάξις}
(\emph{táxis} `order, arrangement; the prefix \emph{syn-} means `together')

This etymology gives little clue to just what syntacticians do, however. This is not merely a consequence of the ``generative revolution'', as the predecessors of transformational grammars associated with Zellig Harris and Noam Chomsky were also more than theories of arrangement, but also instantiate the notion of derivation \citep[e.g.,][]{Post1943}.

\subsection{?}

\subsection{Units of description}
\subsubsection{Segment inventory}
\subsubsection{Surface segment sequences}
\subsubsection{Underlying segment sequences}

\subsection{The morph}

The notion of blocking in non-derived environments (\citealp[163]{Kiparsky1973a}, \citeyear[152]{Kiparsky1982a}, \citealp{Mascaro1976}) is well-known, but \citet{Hall2006} also amasses evidence for phonological processes restricted to non-derived environments. One of the most famous examples is the distribution of \emph{ich-laut} [ç] and \emph{ach-laut} [x] in German \citep{Bloomfield1930}. As shown in (\label{ichach}), [x] appears only before back vowels; in all other contexts, the only dorsal fricative is [ç].

\begin{example}[German \emph{ich}- and \emph{ach-laut}]
\begin{tabular}{l l l}
a. & \emph{B}[uːx]          & `book'           \\
   & \emph{T}[ɔx]\emph{ter} & `daughter'       \\
   & \emph{N}[ax]\emph{t}   & `night'          \\
b. & \emph{S}[iç]\emph{t}   & `view'           \\
   & \emph{Sp}[eç]\emph{t}  & `woodpecker'     \\
   & \emph{Ger}[yç]\emph{t} & `rumor'          \\
   & \emph{Kn}[øç]\emph{el} & `ankle, knuckle' \\
   & \emph{Fl}[ɛç]\emph{e}  & `surface'        \\
\end{tabular}
\end{example}

%a. & \emph{B}[uːx]          & \emph{B}[yːç]\emph{er} & `book' \\
%   & \emph{L}[ɔx]           & \emph{L}[øç]\emph{er}  & `hole' \\
%%   &\emph{T}[ɔx]\emph{ter} & \emph{T}[øç]\emph{ter}
%   & \emph{N}[ax]\emph{t}   & \emph{N}[ɛç]\emph{te} & `night' \\

@@

%\emph{Mas}[oːx]-\emph{Mas}
\footnote{Examples like \emph{Mas}[oːç]\emph{ist} `masochist', \emph{Eun}[uːç]\emph{ismus} `eunichism', first noted by \citet{Merchant1994}, suggest that this should also be restricted to assimilation within the same foot \citep[226f.]{Jensen2000}.}

%\emph{Mas}[oːx]-\emph{Mas}[oːç]\emph{ist}

The concept of non-derived environment blocking

@@

\subsection{Prosodic parsing}
\subsubsection{Syllabification}
\subsubsection{Autosegmental tiers}

\subsection{Rule application}
\subsubsection{Violation detection}
\subsubsection{Rule exceptionality}

\section{Consequences of the model}

\subsection{Gradience}
\subsubsection{Probabilistic well-formedness}
\subsubsection{Cumulativity}
\subsubsection{External factors}

\subsection{Static phonotactics}
\subsubsection{Statistical insensitivity}
\subsubsection{Saussurean arbitrariness}

\subsection{Order of acquisition}
\subsubsection{Lexical acquisition}
\subsubsection{Prosodic parsing}
\subsubsection{Rule application}

%\subsubsection{Exceptionality}

>>>>

\chapter{A generative theory of phonotactic knowledge and acquisition}
\label{intro}

Syntax can hardly be described as a theory of word ``arrangement''; it would be inconceivable for syntacticians to engage in a lengthy debate about whether some word sequence is permitted in some language. Yet it is possible for two reasonable phonologists to dispute whether [k.p] is a permissible medial consonant cluster in English. While lexical entries are thought to consist of segments, and segments to consist of feature specifications, the phonological form of a word like \emph{spectre} is not ``generated'', in any relevant sense, by the concatenation of segments /s/, /p/, and so on, or by the concatenation of syllables \{spɛk\}$_{\sigma}$ and \{tɚ\}$_{\sigma}$. It would be possible to posit ``lexical concatenation rules'', on analogy with the phrase structure rules of syntax, but it is unclear how the strings produced would be linked with meanings, or how such a system would distinguish between, e.g., \emph{brick} and meaningless \emph{blick}.

The more appealing alternative is that the phonological form of \emph{spectre}, whatever it is, is an atom of unit of lexical memory. It remains to account for any restrictions on the contents of underlying forms. The theory of \emph{phonotactics} (which is related to \emph{syntax} through the Greek root \emph{táxis} `order') is concerned with these restrictions and how they are related to the mappings between underlying and surface forms for which the phonological component is responsible.

%\footnote{It is tempting, however, to describe binding principles as ``syntactics''.}

I believe that the boundaries of this knowledge

The boundaries of this knowledge
and what might be acquired.
These are not unrelated issues:

\section{\emph{Táxis} and generativity}
%\emph{τάξις}

(\emph{táxis} `order, arrangement'; the prefix \emph{syn-} means `together')

This etymology is almost completley uninformative about the modern study of syntax. 
The notion of derivation, most associated with the transformational grammars of Zellig Harris and Noam Chomsky

This etymology gives little clue to just what syntacticians do, however. This is not merely a consequence of the ``generative revolution'', as the predecessors of transformational grammars associated with Zellig Harris and Noam Chomsky were also more than theories of arrangement, but also instantiate the notion of derivation.

\subsection{Units of phonotactic description}

\subsubsection{Segments}

\subsubsection{Underlying representations}

\subsubsection{Surface sequences}

% discussion of Ernestus & Baayen 2003, Becker et al. 2011

The notion of blocking in non-derived environments (\citealp[163]{Kiparsky1973a}, \citeyear[152]{Kiparsky1982a}, \citealp{Mascaro1976}) is well-known, but \citet{Hall2006} also amasses evidence for phonological processes restricted to non-derived environments. One of the most famous examples is the distribution of \emph{ich-laut} [ç] and \emph{ach-laut} [x] in German \citep{Bloomfield1930}. The dorsal fricative is [x] before back vowels and[ç] in other contexts.

\begin{example}[German \emph{ich}- and \emph{ach-laut}]
\begin{tabular}{l l l}
a. & [buːx]   & `book'           \\
   & [tɔxtər] & `daughter'       \\
   & [naxt]   & `night'          \\
b. & [siçt]   & `view'           \\
   & [ʃpeçt]  & `woodpecker'     \\
   & [ɡərʏçt] & `rumor'          \\
   & [knøçəl] & `ankle, knuckle' \\
   & [flɛçə]  & `surface'        \\
\end{tabular}
\end{example}

\emph{Umlaut}, the fronting (and raising) of back vowels in certain morphological contexts, produces the front variant of the dorsal fricative; e.g., [lɔx]-[løçər] `hole-holes'.
%\emph{B}[uːx]-\emph{B}[yːç]\emph{er} `book-books',

@@

%\emph{Mas}[oːx]-\emph{Mas}
\footnote{Examples like \emph{Mas}[oːç]\emph{ist} `masochist', \emph{Eun}[uːç]\emph{ismus} `eunichism', first noted by \citet{Merchant1994}, suggest that this should also be restricted to assimilation within the same foot \citep[226f.]{Jensen2000}.}
%\emph{Mas}[oːx]-\emph{Mas}[oːç]\emph{ist}

@@

\subsection{Syllabification}

\subsection{Rule application and occultation}

\subsection{Detecting violations}

\subsection{Exceptionality}
% autosegments

\section{Predictions of the model}

\subsection{Gradience}
\subsubsection{Probabilistic well-formedness}
\subsubsection{External factors}

\subsection{Static phonotactics}
\subsubsection{Insensitivity to statistics}
\subsubsection{Saussurean arbitrariness}

\subsection{Order of acquisition}

A point of departure is a review of phonotactic acquisition by \citet{Hayes2004b}.

\emph{pure phonotactic learner}
%...
However, \citeauthor{Hayes2004b} ignores the considerable evidence that infants younger than nine months of age---the \emph{terminus ante quem} for the onset of phonotactic knowledge---already have relatively rich and detailed lexical knowledge

A word of caution is in order. An experiment which finds typically-developing infants of a certain age insensitive to an adult-like contrast using a certain task is by no means sufficient evidence to conclude that infants of this age lack this ability. A negative result may simply indicate that the task lacks ecological validity or requires domain-general cognitive resources beyond those of the infants. For instance, \citet{Werker2002} report that 14-month-old infants are insensitive to small phonological differences between novel words, but \citet{Fennell2006} shows that they are sensitive to the same contrasts when the novel words are situated in a more naturalistic naming scenario and cognitive demands are minimized. Other negative findings might be attributed to failure to control for properties of the stimulus, or to an experimental design which lacks sufficient statistical power.

\citet{Jusczyk1993b} native vs. non-native
\citet{Jusczyk1994} no preference for high prob
\citet{Friederici1993}

Finally, \citet{Mattys1999} find that 9-month-old infants treat hetero-organic nasal-stop clusters in nonce words as indications of word juncture, though this effect is small compared to the effect of other cues like primary stress: they do not test younger infants.

\subsubsection{Prosodic parsing}

Newborn infants are already able to distinguish between monosyllabic and bisyllabic words, but these infants are thought to recognize syllables ``holistically'' rather than as sequences at least until 4 months \citep[e.g.,]{Bertoncini1981,Eimas1999,Jusczyk1987}. The earliest evidence for segmental representations comes not from phonotactic preferences, but from infants' ability to dicriminate between familiar words like \emph{cup} and mispronunciations like \emph{*tup} at 7.5 months of age \citep{Jusczyk1995}.

\subsubsection{Phonological processes}

There are very few investigating infants' knowledge of phonological alternations. \citet{White2008} expose 8.5-month-old and 10-month-old infants to an artificial language in which the voicing of fricatives is contrastive, but voiced and voiceless variants of stops are in a complementary distribution, appearing only after vowels (\emph{na-bevi}) and after voiceless consonants (\emph{rot-pevi}), respectively. After familiarization, infants at both ages prefer to listen to stimuli which preserve the complementary distribution over those which disrupt it (e.g., \emph{na poli}, \emph{rot boli}). As \citeauthor{White2008} note, this suggests that infants have grouped \emph{pevi} and \emph{bevi} together and extracted the stop voicing alternation from the artifical language.

\subsubsection{Lexical acquisition}

As first observed by \citet{Darwin1877}, the first words infants recognize are names, their own and those of caretakers. Recent studies suggest that infants learn these names as early as 4 months of age \citep{Bortfeld2005,Mandel1995,Tincoff1999}. Infants as young as 6 months of age have learned the meaning of familiar words \citep{Bergelson2012}. By 8 months of age, infants are able to locate familiar and novel words in utterances \citep{Jusczyk1997,Seidl2006}.
\section{Outline of the dissertation}

The remainder of the dissertation consists of three case studies which provide support for the novel and contentious predictions of the minimal phonotactic model sketched above

Chapter \ref{gradience} considers evidence from wordlikeness rating tasks. It is argued that intermediate well-formedness ratings are obtained whether or not the categories in question are graded. A primitive categorical model of wordlikeness using prosodic representations is outlined, and shown to predict English speakers' gradient wordlikeness judgements as well as state-of-the-art gradient wellformedness models. The gradient models do not contribute any additional coverage once categorical wellformedness is accounted for.

Chapter \ref{turkish} considers the relationship between lexical generalizations, phonological alternations, and speakers' nonce word judgements with a focus on Turkish vowel patterns. It is shown that even exception-filled phonological generalizations have a robust effect on wellformedness judgements, but that statistically reliable phonotactic generalizations go unlearned when they are not derived from phonological alternations.
%Some arguments against Becker et al.

Chapter \ref{clusters} investigates the role of phonological alternations in constraining lexical entries, focusing specifically on medial consonant clusters in English. Static phonotactic constraints previously proposed to describe gaps in the inventory of medial clusters are shown to be statistically unsound. On the other hand, phonological alternations impose robust restrictions on the cluster inventory. The remaining gaps in the cluster inventory are due to the sparse nature of the lexicon, not static phonotactic restrictions.

%% NOTES HERE
%a. & \emph{B}[uːx]          & \emph{B}[yːç]\emph{er} & `book(s)' \\
%   & \emph{L}[ɔx]           & \emph{L}[øç]\emph{er}  & `hole(s)' \\
%   &\emph{T}[ɔx]\emph{ter} & \emph{T}[øç]\emph{ter}
%   & \emph{N}[ax]\emph{t}   & \emph{N}[ɛç]\emph{te} & `night' \\
%
% While the bulk of evidence for detailed phonological entries is found in infants over a year of age \citep[e.g.,]{Werker2002,Fennell2003,Fennell2006,Stager1997,Swingley2000,Zamuner2006},
%9-month-old infants already have learned the predominant stress pattern of their language \citep{Jusczyk1993a}.

### 2012-10-10 2.tex
Writing on front matter, chapters 1-4

@@

In English, [bl] is a permissible onset, but unlike some languages (e.g., Moroccan Arabic \emph{bni} `building', \emph{bnat} `daughters', \emph{bniqa} `closet'), [bn] is not. \citet[][19f.]{Wolf2009} suggest, for instance, that an underlying /bnɪk/ would be realized as [nɪk]; it is also possible to imagine resolution by prothesis---[əbnɪk]---or anapytxis---[bənɪk], and indeed \citet{Davidson2006b} finds that English speakers use all three of these repairs when asked to mimic foreign pronunciations of obstruent-nasal onsets like /bn/.

However, many linguists now regard the above as overly simplistic, for, as \citeauthor{Shademan2006} argues, such accounts draw a categorical boundary between the possible and impossible which fails to match the granularity at which speakers may report ``wordlikeness'' intuitions.

@@

Gradient grammaticality is assumed in the earliest work on generative syntax, \emph{The logical structure of linguistic theory}, in which \citet[132]{LSLT} writes that ``there is little doubt that speakers can fairly consistently order new utterances, never previously heard, with respect to their degree of `belongingness' to the language''. Later, \citet{ASPECTS} proposes that different syntactic violations give rise to different degrees of ungrammaticality. Unlike \citeauthor{Fischer-Jorgensen1952}, however, for \citeauthor{LSLT} this continuum does incorporate a hard-and-fast boundary between the grammatical and ungrammatical: there are no constrasts between grammatical utterances, merely between different degrees of ungrammaticality. For \citeauthor{LSLT}, all grammatical utterances are alike with respect to their grammaticality, but there are many degrees of ungrammaticality \citep[61]{Schutze1996}.

\citet{Halle1962} and \citet{Stanley1967} concern themselves only with categorical wordlikeness contrasts, however. Both authors derive wordlikeness effects from morphophonemic redundancy rules acting on underlying representations. The discussion of \emph{bnick} by \citet[101]{Chomsky1965} is a good example: \citeauthor{Chomsky1965} observe that a consonant before a word-initial stop can only be a liquid in English. A corresponding redundancy rule which specifies a consonant in this position as [$+$\textsc{Liquid}] precludes the derivation of \emph{bnick}, since there is no way to realize the second consonant as a nasal.\footnote{This is not the only redundancy that could rule out \emph{bnick}. For instance, /s/ is the only word-initial consonant that may precede a nasal consonant in English.}

@@

Recent critiques of this syllabification-based model focus on the existence of intermediate wordlikeness ratings \citep[see also][]{Coleman1997,Anttila2008}.

@@

\citet{Albright2003b} gathered wordlikeness judgements to serve as norms for a \emph{wug}-test. 87 items were presented to 20 undergraduate subjects, who rated each word on a seven-point Likert scale. The lowest point on the scale was labeled ``completely bizarre, impossible as an English word'', and that the highest point was labeled ``complete normal, would make a fine English word''.

@@

A possible further extension to the binary baseline would be the introduction of additional levels of wellformedness. While the evaluation has shown that current gradient models do not reliably identify intermediate wellformedness, it does seem possible to identify at least three levels of grammaticality: for instance, one might encode the intuition that \emph{zhlick} [ʒlɪk] is more English-like than \emph{bnick}, though both have unattested onsets. There are precedents for labeling certain attested words as phonotactically ``peripheral'' (see, e.g., the appendices in \citealt{Myers1987} and \citealt{Borowsky1989}); such words are regarded as lexical exceptions to language-general principles of syllabification. If this extends to nonce words, then an intermediate level of grammaticality could be assigned to ``possible'' but formally marked words. Another likely source of additional levels of grammaticality is the cumulative effect of multiple phonotactic violations. While, as \citet{Coleman1997} note, classical Optimality Theory predicts that a nonce word is as ill-formed as its worst deviation from syllable structure, it is possible to imagine that multiple phonotactic violations would result in greater degrees of ill-formedness. The bigram and maxent models make this prediction, as do many others \citep[e.g.,][]{Legendre1990,Levelt2000,Albright2008,Anttila2008,Pater2009b} but despite this, there is still little data demonstrating cumulative effects in wordlikeness tasks.

@@

The findings here also have interesting rammifications for language acquisition. \citet{Saffran1996} famously argues that infants use statistical dependencies between segments to extract words from continuous speech. Among those who ascribe to the Continuity Hypothesis \citep[e.g.,][]{Macnamara1982,Pinker1984,Crain1991,Carey1995,deVilliers2001,Legate2007}, which holds that children acquiring language deploy the same types of linguistic representations as adults, evidence for gradient phonotactic knowledge in infants is evidence for this knowledge in adults, and vis versa. The results here then stand to weaken the hypothesis of \citeauthor{Saffran1996}, as well as the hypothesis that infants acquire a system of phonotactics (gradient or otherwise) before learning of alternations and lexical entries that is a direct prediction of algorithms for learning Optimality Theory grammars \citep{Tesar2004,Hayes2004b}.

%\footnote{The hypothesis that infants acquire a system of phonotactics (gradient or otherwise) before learning of alternations and lexical entries has some traction among formal linguists, for \citet{Hayes2004b} and \citet{Tesar2004} note that is a direct prediction of algorithms for learning Optimality Theory grammars. However, there is extensive evidence that infants who are younger than 9 months, the age at which \citet{Jusczyk1994} argue that the system probabilistic phonotactics comes online, have been demonstrated have already begun extracting words \citep[e.g.,][]{Darwin1877,Mandel1995,Jusczyk1995,Tincoff1999,Jusczyk1999b,Brent2001,Bortfeld2005,Seidl2006,Shukla2011,Bergelson2012} and alternations \citep{White2008} from multiword utterances they encounter.} Each of the tenets of this argument has been subject to serious critique, however.

First, it appears that the youngest treat syllables holistically \citep{Bertoncini1981,Jusczyk1987} and rapidly learn native-language syllable-based phonotactics \citep{Onishi2002,Chambers2003}, suggesting that any co-occurrence statistics should be delimited on units larger than the segments proposed by \citeauthor{Saffran1996}. Secondly, a good deal of the literature has focused on segmentation according to near exceptionless constraints that hold between adjacent syllables. For instance, infants as young as 4.5 months seem to be aware that English nasal codas agree in place with following obstruents \citep{Mattys2001b,Jusczyk2002,Davidson2004}. It might be the case that syllable co-occurrence statistics might be little more than a reflection of infants' learning of categorical ``lexical viability'' constraints \citep{Johnson2003} of the sort also seen in adult speech processing \citep[e.g.,][]{Norris1997}. Further, the effect of these statistical dependencies appear to be filtered by expectations about word stress \citep{Johnson2001,Mattys2001a,Shukla2007}, word length \citep{Lew-Williams2012}, and allophonic generalizations \citep{Hohne1994,Jusczyk1999c}. Finally, and perhaps most importantly, \citet{Gambell2005} find that a word segmentation strategy based only on statistical dependencies performs very poorly on realistic data. The emerging view of the role on statistics seems to be that infants attend to transitional probabilities or an analogue thereof only when they are faced with artificial stimuli with few of the properties of natural language \citep[e.g.,][]{Shukla2007,Lew-Williams2011}. The argument from Continuity is weak, in either direction.

>>>>

%\citet{Saporta1958}
%\citet{Saporta1957}

@@

In English, [bl] is a permissible onset, but unlike some languages (e.g., Moroccan Arabic \emph{bni} `building', \emph{bnat} `daughters', \emph{bniqa} `closet'), [bn] is not. \citet[][19f.]{Wolf2009} suggest, for instance, that an underlying /bnɪk/ would be realized as [nɪk]; it is also possible to imagine resolution by prothesis---[əbnɪk]---or anapytxis---[bənɪk], and indeed \citet{Davidson2006b} finds that English speakers use all three of these repairs when asked to mimic foreign pronunciations of obstruent-nasal onsets like /bn/.\footnote{However, \citet{Davidson2005,Davidson2006a} observes an acoustic and articulatory distinction between ``exscrescent'' echwa found in non-native cluster production and ``lexical'' schwa: the anaptyctic [z${^\textrm{ə}}$k] produced by English speakers attempting to mimic word-initial [zk] is more similar to \emph{scum} than to \emph{succumb}. This may undermine any link between non-native realizations and epenthesis found elsewhere in English (e.g., allomorphs of the regular past tense and noun plural).} However, many linguists now regard the above as overly simplistic, for, as \citeauthor{Shademan2006} argues, such accounts draw a categorical boundary between the possible and impossible which fails to match the granularity at which speakers may report ``wordlikeness'' intuitions.

@@

Gradient grammaticality was a tenet of the earliest work on generative syntax. For instance, \citet[132]{LSLT} writes that ``there is little doubt that speakers can fairly consistently order new utterances, never previously heard, with respect to their degree of `belongingness' to the language''. \citet{ASPECTS} proposes that different syntactic violations give rise to different degrees of ungrammaticality. Unlike \citeauthor{Fischer-Jorgensen1952}, however, for \citeauthor{LSLT} this continuum does incorporate a hard-and-fast boundary between the grammatical and ungrammatical: there are no constrasts between grammatical utterances, merely between different degrees of ungrammaticality. For \citeauthor{LSLT}, all grammatical utterances are alike with respect to their grammaticality, but there are many degrees of ungrammaticality \citep[61]{Schutze1996}.

\citet{SPR,Halle1962} and \citet{Stanley1967} concern themselves only with categorical wordlikeness contrasts, however. Both authors derive wordlikeness effects from morphophonemic redundancy rules acting on underlying representations. The discussion of \emph{bnick} by \citet[101]{Chomsky1965} is a good example: \citeauthor{Chomsky1965} observe that a consonant before a word-initial stop can only be a liquid in English. A corresponding redundancy rule which specifies a consonant in this position as [$+$\textsc{Liquid}] precludes the derivation of \emph{bnick}, since there is no way to realize the second consonant as a nasal.\footnote{This is not the only redundancy that could rule out \emph{bnick}. For instance, /s/ is the only word-initial consonant that may precede a nasal consonant in English.}

@@

Recent critiques of this syllabification-based model focus on the existence of intermediate wordlikeness ratings \citep[see also][]{Coleman1997,Anttila2008a}.

@@

\citet{Albright2003b} gathered wordlikeness judgements to serve as norms for a \emph{wug}-test. 87 items were presented to 24 undergraduate subjects, who rated each word on a seven-point Likert scale. The lowest point on the scale was labeled ``completely bizarre, impossible as an English word'', and that the highest point was labeled ``complete normal, would make a fine English word''.

\begin{table}
\label{counts}
\centering
\begin{tabular}{l r r r}
\toprule
        & subjects & items & observations \\
\midrule
Scholes & 33       & 66    & 2,079        \\
A\&H    & 24       & 88    & 2,112        \\
\bottomrule
\end{tabular}
\caption{Idk.}
\end{table}

@@

A possible further extension to the binary baseline would be the introduction of additional levels of wellformedness. While the evaluation has shown that current gradient models do not reliably identify intermediate wellformedness, it does seem possible to identify at least three levels of grammaticality: for instance, one might encode the intuition that \emph{zhlick} [ʒlɪk] is more English-like than \emph{bnick}, though both have unattested onsets. There are precedents for labeling certain attested words as phonotactically ``peripheral'' (see, e.g., the appendices in \citealt{Myers1987} and \citealt{Borowsky1989}); such words are regarded as lexical exceptions to language-general principles of syllabification. If this extends to nonce words, then an intermediate level of grammaticality could be assigned to ``possible'' but formally marked words. Another likely source of additional levels of grammaticality is the cumulative effect of multiple phonotactic violations. While, as \citet{Coleman1997} note, classical Optimality Theory predicts that a nonce word is as ill-formed as its worst deviation from syllable structure, it is possible to imagine that multiple phonotactic violations would result in greater degrees of ill-formedness. The bigram and maxent models make this prediction, as do many others \citep[e.g.,][]{Legendre1990,Levelt2000,Albright2008,Anttila2008a,Pater2009b} but despite this, there is still little data demonstrating cumulative effects in wordlikeness tasks.

@@

The weak empirical status of gradient phonotactic knowledge as reflected in adults has rammifications for language acquisition under the hypothesis that that infants acquiring language deploy the same representations as adults \citep[e.g.,][]{Macnamara1982,Pinker1984,Crain1991,Carey1995,deVilliers2001,Legate2007}. Gradient wordlikeness judgements in adults would provide support for claims that infants recognize statistical(inherently gradient) dependencies between segments \citep{Jusczyk1994} and use these to segment words \citep{Saffran1996}. An emerging consensus suggests, however, that infants attend to transitional probabilities primarily in the absence of grammatical cues \citep{Gambell2005,Hohne1994,Johnson2001,Jusczyk1999c,Lignos2012,Mattys2001a,Shukla2007,Lew-Williams2012}. The vacuous nature of current evidence for gradient phonotactic knowledge in adults further weakens any hypothesis that would link statistical learning in infants to adults' behaviors.

%For instance, infants as young as 4.5 months seem to be aware that English nasal codas agree in place with following obstruents \citep{Mattys2001b,Jusczyk2002,Davidson2004}. 
%It might be the case that syllable co-occurrence statistics might be little more than a reflection of infants' learning of categorical ``lexical viability'' constraints \citep{Johnson2003} of the sort also seen in adult speech processing \citep[e.g.,][]{Norris1997}.
